### 2018-07-17 Writeup/PERT_New.tex
Update the tests
Update the writeup

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{framed}
\usepackage{natbib}
\usepackage{float, subfig}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{grffile}
\usepackage{sidecap}
\usepackage{pbox}
\usepackage{algorithm}
\usepackage{longtable}
\usepackage[noend]{algpseudocode}

@@

\renewcommand{\P}{{\mathbb P}}
\newcommand{\E}{{\mathbb E}}
\newcommand{\R}{{\mathbb R}}
\renewcommand{\Re}{{\mathbb R}}
\newcommand{\mbf}{\mathbf}

@@

	The deterministic project crashing optimization problem has been known since the 1960s \cite{fulkerson1961network, kelley1961criticalpath}. Suppose the activity network is represented by a directed graph \(\mathcal{G} = (I,\mathcal{A})\), where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\). The arc \((i,j) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(j\). We create a dummy activity \(N\) to represent the end of entire project, which should succeed every activity \(i \in I\). \\

@@

	\begin{subequations} \label{prob2:static}

@@

		\min \quad & t_N &\\

@@

	In this formulation, \(t_i\) represents the starting time of activity \(i \in I\). We aim to minimize the project span, which is the starting time of the dummy activity, \(t_N\). Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finishing time of activity \(i\) is \(t_i + D_i (1- \sum_{j \in J_i} x_{ij}e_{ij})\). Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity. \\

@@

	In our problem, we assume at most one stochastic disruption can occur in the project span, while the time of such disruption is a random variable. We also assume for each activity \(i \in I\), the crashing decision decision for that activity needs to be made prior to the start of that activity, and cannot be changed after that. We assume that the disruption does not affect the activities that have already started but changes the length of activities starting after it according to some given distributions. We assume there is a discrete finite set of scenarios indexed by \(\Omega\). It is usually hard to compute the recourse function directly when some of its parameters are distributed according to continuous distributions, and SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}. \\

@@

	Since there is at most one disruption, we can model the problem as a two-stage stochastic mixed integer program. Notice that the definition of the first stage is different from the traditional stochastic program setting. Here the first stage contains decisions through completion of the project if no disruption occurs and the second stage characterize the decisions for each realization of the disruption. This means that the first stage decision variables are carried out until the disruption, if it ever occurs, and after the disruption, depending on the scenario realized, the scenario-specific recourse decisions are executed.\\

@@

		\(S_{ij}^\omega\) & \(\qquad\) & binary term to linearize the bilinear term \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&\\

@@

	\noi The extensive formulation of the two-stage stochastic program is shown as formulation~(\ref{prob2:extensive}):
	\begin{subequations} \label{prob2:extensive}

@@

		\min \quad & \sum_{\omega \in \Omega} p^\omega t_N^\omega + p^0 t_N \\
		\text{s.t.} \quad & t_N^\omega \geq t_i^\omega \qquad \qquad \forall \,i \in I, \omega \in \Omega \\
		& t_N \geq t_i \qquad \qquad \label{cons:tN}\\
		& t_i^\omega \geq 0 \qquad \qquad \forall \,i \in I, \omega \in \Omega\\
		& H^\omega - (1 - G_i^\omega) M \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:F}\\
		& H^\omega + G_i^\omega M \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:G}\\
		& t_i^\omega + G_i^\omega M \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tf1}\\
		& t_i^\omega - G_i^\omega M \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tf2}\\
		& x_{ij}^\omega + G_i^\omega \geq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf1}\\
		& x_{ij}^\omega - G_i^\omega \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf2}\\
		& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
		& \sum_{j \in J_i} x_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:crashLim}\\
		& \sum_{i \in I}\sum_{j \in J_i} b_jx_{ij}^\omega \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:budget}\\
		& S_{ij}^\omega \leq G_i^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
		& S_{ij}^\omega \leq x_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
		& S_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\

@@

		& 0 \leq S_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\

@@

	In model~\eqref{prob2:extensive}, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability. Variables \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint \eqref{cons:F}-\eqref{cons:G}) and \(M\) is a large number to enforce the logic relationships. This is important in our problem setting because the duration of each activity depends on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}). For this duration constraint, the original expression of the duration of activity \(i\) is \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\). This contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which is linearized by introducing a binary variable \(S_{ij}^\omega\) and bounding it by constraints \eqref{cons:linearize1}-\eqref{cons:linearize3}.\\

@@

	We use a set of non-anticipativity constraints \eqref{cons:tf1}-\eqref{cons:xf2}, different from ones used in a traditional stochastic programming because the first stage decision variables here spans the entire time horizon. These logic constraints ensure that the decisions made before the disruption time in each scenario are the same as the nominal decisions before the same time point.

\section{Special Cases} \label{sec:examples}
	In this section we show a serial example to illustrate the nature of the project crashing problem under stochastic disruption. From this serial network example we show that it might be optimal to delay the start of some activities, and thus justify the formulation in model~\eqref{prob2:extensive}. \\
	Suppose we have a project with three activities in a serial network form. Activity 1 must finish before the start of activity 2 and the activity 2 must finish before the start of activity 3. The structure of the project is displayed as follows. We add a dummy activity ``N" to represent the end of the project. The total crashing budget is \(1\) and the allowed amount of crashing a single activity is between \(0\) and \(1\). 

@@

	\noi So, \(I=\{1,2,3,N\}\), and \(D_1=9\), \(D_2=10\), and \(D_3=7\). The probability of the disruption not occurring is \(p^0=\frac{1}{2}\), and if a disruption occurs, it will occur at the time \(H^2 = 9.1\). The set of scenario \(\Omega = \{1\}\), where scenario 1 represents the disruption scenario. Suppose the disruption changes \(D_2=10\) to \(3\), a.k.a. \(d_2^1 = -7\), and not affect activity 3. We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\), spend the entire budget to crash activity 3 if the disruption occurs, and spend the entire budget to crash activity 2 if the disruption does not occur. The expected total project span is 18.35. If we force the condition that the starting time of activities cannot be delayed, we cannot observe whether the disruption happens or not prior to the start of activity 2. There is only one possible situation where three activities have the duration as 9, 10 and 7. All resources should be allocated to activity 2 and the total project span is 21, which is larger than the expected total project span if it is allowed to delay the starting time of some activities. In this example, a disruption may reduce the duration of some activities and delaying by a small amount allows us to realize that reduction in time.\\
	Even if the disruption can only lengthen an activity's duration, it is still beneficial to delay the start of some activities under some circumstances. This means a small delay of some activity may gain the information regarding the disruption, which can decrease the project span. To see this, we again consider the serial network of Figure~\ref{fig:serial3}. We assume the nominal durations, and the stochastic disruption, are identical to those above. If the disruption occurs, the durations of activities change by \(d_2^1=0.1\) and \(d_3^1 = 6\). For this example, if no delay is allowed, the optimal decision is to have \(x_2 = 1\) and the optimal objective value is 24. If we delay the starting time of the activity 2 to \(t_2 = 9.1\) so that the disruption can be observed before we commit resources to activity 2, the optimal expected total project span is 23.4. \\

@@

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{amssymb}
\usepackage{accents}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{framed}
\usepackage{natbib}
\usepackage{float, subfig}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{grffile}
\usepackage{sidecap}
\usepackage{pbox}
\usepackage{algorithm}
\usepackage{longtable}
\usepackage[noend]{algpseudocode}

@@

\renewcommand{\P}{{\mathbb P}}
\newcommand{\E}{{\mathbb E}}
\newcommand{\R}{{\mathbb R}}
\renewcommand{\Re}{{\mathbb R}}
\newcommand{\mbf}{\mathbf}
\renewcommand{\underbar}{\underaccent{\bar}}

@@

	The deterministic project crashing optimization problem has been known since the 1960s \cite{fulkerson1961network, kelley1961criticalpath}. Suppose the activity network is represented by a directed graph \(\mathcal{G} = (I,\mathcal{A})\), where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\). The arc \((i,j) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(j\). We create two dummy activities \(S\) and \(T\) to represent the start and the end of entire project. \(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \). \\

@@

	\begin{subequations} \label{prob:static}

@@

		\min \quad & t_T &\\

@@

	In this formulation, \(t_i\) represents the starting time of activity \(i \in I\). We aim to minimize the project span, which is the starting time of the terminal activity, \(t_T\). Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finishing time of activity \(i\) is \(t_i + D_i (1- \sum_{j \in J_i} x_{ij}e_{ij})\). Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity. \\

@@

	In our problem, we assume at most one stochastic disruption can occur at a random time in the project span. We also assume for each activity \(i \in I\), the crashing decision for that activity needs to be made at the start of that activity, and cannot be changed afterwards. The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution. It is usually hard to compute the recourse function directly when parameters are distributed according to continuous distributions, and therefore SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}. In this paper, we assume there is a discrete finite set of scenarios indexed by \(\omega \in \Omega\). For each scenario \(\\omega\), the random realization of parameters, \(\xi^\omega\), consists of the timing of disruption, \(H\), and the changed duration of each activity, \(d_i, \forall i \in I\). \\

@@

	If there is at most one disruption, we can model the problem as a two-stage stochastic mixed integer program. The definition of our first stage is different from the traditional stochastic program setting. Here the first stage contains decisions through completion of the project if no disruption occurs and the second stage characterizes the decisions for each realization of the disruption. This means that the first stage decision variables are carried out until the disruption, if it ever occurs, and after the disruption, the scenario-specific recourse decisions are executed.\\

@@

		\(z_{ij}^\omega\) & \(\qquad\) & binary term to linearize the bilinear term \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&\\

@@

	\noi The extensive formulation of the two-stage stochastic program is shown as formulation~\eqref{prob:extensive}:
	\begin{subequations} \label{prob:extensive}

@@

		\min \quad & p^0 t_T + \sum_{\omega \in \Omega} p^\omega t_T^\omega \\
		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:Sep}\\
		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:Budget}\\
		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:SingleBudget}\\
		& H^\omega + G_i^\omega M \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:G1}\\
		& H^\omega - (1 - G_i^\omega) M \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:G2}\\
		& t_i^\omega + G_i^\omega M_t \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tG1}\\
		& t_i^\omega - G_i^\omega M_t \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tG2}\\
		& x_{ij}^\omega + G_i^\omega \geq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xG1}\\
		& x_{ij}^\omega - G_i^\omega \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xG2}\\
		& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} z_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:scenSep}\\
		& \sum_{j \in J_i} x_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:scenBudget1}\\
		& \sum_{i \in I}\sum_{j \in J_i} b_{ij}x_{ij}^\omega \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:scenBudget}\\
		& z_{ij}^\omega \leq G_i^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
		& z_{ij}^\omega \leq x_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
		& z_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
		& t_i \geq 0 \qquad \qquad \forall \,i \in I \label{cons:nonnegt}\\

@@

		& 0 \leq z_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\

@@

	In model~\eqref{prob:extensive}, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability. We keep the constraints~\eqref{cons:dSep}-\eqref{cons:dSingleBudget} for the nominal scenario as~\eqref{cons:Sep}-\eqref{cons:SingleBudget}. In constraints~\eqref{cons:G1}-\eqref{cons:G2}, variables \(G^\omega_i\) takes value \(1\) if activity \(i\) starts after the disruption time; otherwise it takes value 0, and \(M\) is a large number to enforce this logic relationships. This is important in our problem setting because the duration of each activity depends on its temporal relationship to the disruption time, which is reflected in constraint~\eqref{cons:scenSep}. Also we have to ensure that the decisions made before the disruption time in each scenario are the same as the nominal decisions. Therefore, we set up non-anticipativity constraints~\eqref{cons:tG1}-\eqref{cons:xG2}. For each scenario, the duration of activity \(i\) becomes \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\), which expands to the form of constraint~\eqref{cons:scenSep}. If \(G_i^\omega = 0\), which means activity \(i\) starts before the disruption time of scenario \(\omega\), this expression is the same as \(D_i (1 - \sum_{j \in J_i} e_{ij}x_{ij})\) since \(x_{ij} = x_{ij}^\omega\) is enforced by constraints~\eqref{cons:xG1} and~\eqref{cons:xG2}. If \(G_i^\omega = 1\), then the duration of activity \(i\) is changed to \(D_i + d_i^\omega\). The expression \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\) contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which can be linearized by introducing a binary variable \(z_{ij}^\omega\) and constraints \eqref{cons:linearize1}-\eqref{cons:linearize3}.

\section{Illustration of Problem Properties via Examples} \label{sec:examples}
	In this section we show a serial example to illustrate the nature of the project crashing problem under stochastic disruption, which is different from the deterministic problem. In the deterministic project crashing problem, all activities on the critical path should start as soon as possible. However, with a stochastic disruption, it might be optimal to delay the start of some activities. Therefore, it is necessary to have decision variable \(t_i, \forall i \in I\) in model~\eqref{prob:extensive} in addition to the crashing decision variable \(x_{ij}, \forall i \in I, j \in J_i\). \\

@@

	It is obvious that the delay can possibly be beneficial if \(d_i^\omega < 0\) for some \(i \in I\) and \(\omega \in \Omega\). We use a serial activity network to show the possibility of beneficial delay, even if all activities are lengthened by the disruption, a.k.a., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\). Suppose we have a project with three activities in a serial network form. Activity 1 must finish before the start of activity 2 and the activity 2 must finish before the start of activity 3. The structure of the project is displayed as follows. We add a dummy activity ``T" to represent the end of the project. The total crashing budget is \(1\). 

@@

	\noi In this example, \(I=\{1,2,3,T\}\), \(D_1=9\), \(D_2=10\), and \(D_3=7\). There is only one crashing option for each activity, so we omit the subscript to index the crashing options. We use \(e_i = 0.5\) for all \(i \in I\). The probability of the disruption not occurring is \(p^0=\frac{1}{2}\), and if a disruption occurs, it will occur at the time \(H^2 = 9.1\). The set of scenario \(\Omega = \{1\}\), where scenario 1 represents the disruption scenario. Suppose the disruption does not affect activity 1, \(d_1^1 = 0\), increases the duration of activity 2 by \(0.1\), \(d_2^1 = 0.1\), and increases the duration of activity 3 by \(6\), \(d_3^1 = 6\). We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\). There we are able to observe whether the disruption happens. If the disruption occurs, it is optimal to spend the entire budget to crash activity 3, and otherwise it is optimal to crash activity 2 with \(1\) amount of resource. The expected total project span is \(23.4\), as the optimal project span given no disruption is \(21.1\) and that under disruption is \(25.7\). If every activity starts as soon as possible, like in the deterministic problem, we cannot observe whether the disruption happens or not prior to the start of activity 2. Under this condition, the best solution is to crash activity 2 with \(1\) amount of crashing resource, and the optimal expected project span is \(24\), larger than \(23.4\). \\

@@

	In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path. We present a following example to showcase this property. Suppose we have a two-activity serial network, and the disruption time follows a probability distribution shown in Figure~\ref{fig:2act}. The nominal durations of two activities are \(D_1 = 3, D_2 = 4\). The disruption does not affect the duration of activity 1, as \(d_1 = 0\), and lengthens the activity 2 by a random variable distributed in a uniform distribution with upper bound \(10\) and lower bound \(0\), as \(d_2 \sim \mathcal{U}(0,10)\). The crashing option setting is the same as the previous example, as there is only one crashing option for each activity and \(e_i = 0.5, \forall i \in I\). The total budget \(B = 1\).
			\includegraphics[width=0.8\textwidth]{2act}
			\caption{Left: an illustration of a 2-activity project; right: probability distribution function of disruption time.}
			\label{fig:2act}
	\noi In this example, the optimal solution is to crash activity 1 with one unit of resource, i.e.\,\(x_1 = 1, x_2 = 0\). Activity 1 starts at time \(t_1 = 0\) and activity 2 starts at time \(t_2 = 1.5\). The optimal expected project span is \(\mathbb{E}[t_T] = 6.5\). We can compare an alternative solution which crash activity 2 with one unit of resource, which has a longer expected duration. Crashing activity 2 matches the intuition from the deterministic case where on the critical path the activities with longer expected duration are prioritized. However, in this case with a stochastic disruption, the latter solution (\(t_1 = 0, t_2 = 3, x_1 = 0, x_2 = 1\)) yields a longer expected project span as \(\mathbb{E}[t_T] = 7.5\). The reason behind this gap is that by crashing activity 1 with one unit amount of resource, the probability of activity 2 starting before the disruption increases to \(0.8\), which prevents activity 2 from seeing the increased duration. \\
	These examples above indicate that the crashing optimization problem with stochastic disruption has complicated nature. The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
	\textcolor{blue}{Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method. }
	Model~\eqref{prob:extensive} is a two-stage stochastic mixed integer program (2SMIP). If we attempt to decompose it into a master problem~\eqref{prob:masterOri} and scenario-specific subproblems~\eqref{prob:subOri}, the state variables \(t\) and \(x\) are all continuous and binary variables exist in the recourse problems. The recourse problems become nonconvex. Most of previous literature of stochastic mixed integer programming assumes a special structure or property which cannot be applied to our problem setting. For example, Sherali/Fracticelli, Sen/Higle, Ntaimo/Sen, Sherali/Zhu, Sen/Sherali, Gade/Kucukyavuz/Sen solve 2SMIPs with pure binary first stage variables using sequential convex approximation of recourse by a branch-and-cut process framework where disjunctive cuts or Gomory cuts are added. Ahmed/Sun/Zou assumes state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function. Caroe/Tind solves a more general case of 2SMIP by using the MIP duality theory but the practical tractability is not optimistic. 
	\begin{subequations}
		\label{prob:masterOri}
		(M) \quad \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega(t,x)\\
		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:MSep}\\
		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:MBudget}\\
		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:MSingleBudget}\\
	\begin{subequations}
		\label{prob:subOri}
		(S^\omega) \qquad f^\omega(\hat{t},\hat{x}) = \min \quad & t_T \\
		& H^\omega + G_i M \geq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:sG1}\\
		& H^\omega - (1 - G_i) M \leq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:sG2}\\
		& t_i + G_i M_t \geq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:stG1}\\
		& t_i - G_i M_t \leq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:stG2}\\
		& x_{ij} + G_i \geq \hat{x}_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sxG1}\\
		& x_{ij} - G_i \leq \hat{x}_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sxG2}\\
		& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} z_{ij} \nonumber \\ 
		& \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:subSep}\\
		& \sum_{j \in J_i} x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:subBudget1}\\
		& \sum_{i \in I}\sum_{j \in J_i} b_{ij}x_{ij} \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:subBudget}\\
		& z_{ij} \leq G_i \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sublinearize1}\\
		& z_{ij} \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sublinearize2}\\
		& z_{ij} \geq G_i + x_{ij} - 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sublinearize3}\\
		& t_i \geq H^\omega G_i \qquad \qquad \forall\, i \in I, \omega \in \Omega \\
		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
		& 0 \leq z_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
		& G_i \in \{0,1\}. \qquad \qquad \forall \,i \in I, \omega \in \Omega. \label{cons:subInt}
	We can relax the integrality constraints~\eqref{cons:subInt} and solve the subproblem to obtain Benders' cuts. Although those Benders' cuts are no longer a tight approximation of the recourse function \(f^\omega(x,t), \forall \omega \in \Omega\), they still provide a valid lower bound. On the other hand, in each iteration of the Benders' decomposition, the upper bound can be obtained by solving the subproblems~\eqref{prob:subOri}, given a first stage solution. We observe that a smaller \(M\) yields a tighter gap between the upper bound and the lower bound, because we can rewrite constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} as:
	\begin{equation}
		(\hat{t}_i - H^\omega)/M \leq G_i \leq (\hat{t}_i - H^\omega)/M + 1
	\end{equation}
	and \(G_i\) can take a wider range of value when \(M\) is larger. Therefore, sequentially tightening \(M\) is helpful to generate a tighter lower bound as the algorithm progresses. Eventually, if for a scenario we can fix the \(G_i\) for all \(i \in I\) to either 0 or 1, the Benders' cuts will be tight.\\
	From now on we assume the scenarios \(\omega \in \Omega\) are ordered according to their time \(H^\omega\) in an ascending order. We can also observe that if we know \(\hat{t}_i \geq H^{\omega'_i}\) for some \(\omega'_i\), \(G_i\) has to take value 1 in all subproblem \(S^\omega\) where \(\omega < \omega'_i\). On the other hand if we know \(\hat{t}_i \leq H^{\omega'_i}\) for some \(\omega'_i\), \(G_i\) has to take value 0 in all subproblem \(S^\omega\) where \(\omega > \omega'_i\). These observations inform us that by bounding the value of first stage variable \(t_i,\ \forall i \in I\), we can determine the value of \(G_i\) in many subproblems, which strengthens the Benders' cuts.\\
	We propose a decomposition algorithm to solve model~\eqref{prob:extensive}. Our method partitions the continuous feasible region of the master problem by introducing of a set of binary variables. As we refine the partition of \(t\)-space, we can generate tightened Benders' cuts to approximate the recourse function. For any crashing optimization problem, we can bound the first stage \(t_i\) variables by lower bound \(0\) and upper bound \(T_{\max} = H^{|\Omega|} + t_T^0\), where \(t_T^0\) is the longest \(S\)-\(T\) path of activity network \(\mathcal{G} = (I,\mathcal{A})\) and the arc length of \((i,j) \in \mathcal{A}\) equals to \(D_i\). This means that suppose the optimal solution of model~\eqref{prob:extensive} is denoted as \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\), the latter two representing the scenario specific starting time and crashing decisions, we have:
	\begin{proposition} \label{prop:bounds}
		 \(t^*_i \in [0,T_{\max}],\ \forall i \in I\).
	\end{proposition}
	\begin{proof}
		Constraint~\eqref{cons:nonnegt} enforces the lower bound of this proposition. \\
		To derive the upper bound, 
		we first establish a feasible solution \(\tilde{t}_i = H^{|\Omega|} + t^0_i,\ \forall i \in I\), \(\tilde{x}_{ij} = 0,\ \forall i \in I, j \in J_i\) and \(\tilde{G}_i^\omega = 1,\ \forall i \in I, \omega \in \Omega\), where \(t^0_i\) represents the length of the longest \(S\)-\(i\) path of \(\mathcal{G}\). 
		If we assume that there exists some \(i \in \tilde{I}\) such that \(t_i^* > T_{\max}\), we know \(T \in \tilde{I}\). There, we can keep \(x^*\), \(G^{*,\omega}\), \(t^{*,\omega}\) and \(x^{*,\omega}\) for all \(\omega \in \Omega\) the same, and replace the \(t_i^*\) by \(\tilde{t}_i\) for all \(i \in \tilde{I}\) without violating any constraints. This yields another feasible solution which has a smaller value of \(t_T^*\) since \(T \in \tilde{I}, \tilde{t}_T = T_{\max} < t_T^*\). Therefore the new objective value obtained by this feasible solution is smaller, which contradicts the assumption that \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\) is an optimal solution.
	\end{proof}
	\noi Proposition~\ref{prop:bounds} indicates that all \(t_i,\ \forall i \in I\) are bounded on an interval \([0,T_{\max}]\). Since there are precedence relationships between activities, the possible range of different activities' starting time can be further limited. We first set up two parameters \(H^0 = 0\) and \(H^{|\Omega| + 1} = T_{\max}\) and then define a partition of this interval for each \(i \in I\) to exploit this limitation as follows:
	\begin{definition}
		For an activity \(i \in I\), the partition of interval \([0,T_{\max}]\) is denoted by \(\mathcal{P}\), which is an ordered set of two-element tuples \((\bar{\omega}^q,\underbar{\omega}^q)\), which is indexed by \(q \in \mathcal{Q}\) and corresponds to the upper bound scenario index and the lower bound scenario index. The partition has the following properties:
			\item \(\underbar{\omega}^1 = 0\)
			\item \(\bar{\omega}^{|\mathcal{Q}|} = T_{\max}\)
			\item \(\bar{\omega}^q = \underbar{\omega}^{q + 1}\).
	\end{definition}
	\noi A simple example of such partition can be illustrated in Figure~\ref{fig:simplePart}. In this example we have five scenarios \(\Omega = \{1,2,3,4,5\}\), ordered by the disruption time. The partition has three elements, each illustrated by a box with dashed lines and represent a part of the interval. For partition element \(1\), the lower bound scenario index is \(0\) and the upper bound scenario index is \(2\), which means the range corresponding to it is lower bounded by \(H^0 = 0\) and upper bounded by \(H^2\).
		\includegraphics[width=0.8\textwidth]{simplePart}
		\caption{An illustration of partition on interval \([0,T_{\max}]\).}
		\label{fig:simplePart}
	Here we present the modified master problem and subproblems with the addition of partition:
	\begin{subequations}
			(M_P) \quad \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\
			\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:MpSep}\\
			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:MpBudget}\\
			& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:MpSingleBudget}\\
			& \sum_{q \in \mathcal{Q}_i} y^q_i = 1 \qquad \qquad \forall i \in I \\
			& \sum_{q \in \mathcal{Q}_i} \underbar{H}_i^{q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} \bar{H}_i^{q} y_i^{q} \qquad \qquad \forall i \in I\\
			& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) \nonumber \\
